Acid-induced protein gels: from gelation to stress-induced failure

### 2015-06-04 talk_Zurich.tex
Behaviour of the food
Biogel, food and coauthors at the end

\begin{frame}{Mouth feel}
\begin{columns}
\column{0.8\textwidth}
\begin{itemize}
\item A very complex, multidimensional sensation
\item Food behaviour at large deformation is important
\item How does food break into pieces ?
\end{itemize}
\column{0.2\textwidth}
\includegraphics[width=\textwidth]{violon}
\end{columns}

@@

\begin{frame}{What about biogels? \textup{\normalsize(physical gels
$E_{bond}\gg k_B T$)}}
\begin{tabu}{cX[c]c}
\includegraphics[height=0.3\textheight]{cell_mech} &
\includegraphics[height=0.3\textheight]{electrophoresis} &
\includegraphics[height=0.3\textheight]{cosmetics} \\
Cell mechanics & Electrophoresis & Cosmetics\\
\end{tabu}
\begin{tabu}{X[c]X[c]}
\includegraphics[height=0.3\textheight]{bacterial_culture} &
\includegraphics[height=0.3\textheight]{food} \\
Bacterial culture & Food\\
\end{tabu}

\begin{footnotesize}
\begin{block}{Sources}
\begin{tabu}{lXl}
Wikimedia Commons & www.madaboutscience.com & www.keautystore.com\\
\end{tabu}
\end{block}
\end{footnotesize}
\end{frame}
%
%
%
%\begin{frame}{Fundamental issues in biogels}
%\begin{itemize}
%\item Linear elasticity is not well understood \textit{\scriptsize Gardel et al. Science 2004}
%\item Strain and stress stiffening \textit{\scriptsize Storm et al. Nature 2005}
%\item Fractures \textit{\scriptsize Bonn et al. Science 1998, Baumberger et al. Nature Material 2006}
%\item Mechanical instabilities and morphogenesis \textit{\scriptsize Shyer et al. Science 2013}
%\end{itemize}
%\begin{tabu}{X[c]X[c]}
%\includegraphics[height=6\baselineskip]{Bonn_fracture} &
%\includegraphics[height=6\baselineskip]{Villi_sq}
%\end{tabu}
%\begin{block}{Our questions}
%\begin{itemize}
%\item What is the behaviour of a biogel under shear deep into the nonlinear regime?
%\item What is the role of the solvent in mechanical instabilities?
%\end{itemize}
%\end{block}
%\end{frame}

@@

>>>>

\begin{frame}{Mouth feel}
\begin{columns}
\column{0.8\textwidth}
\begin{itemize}
\item A very complex, multidimensional sensation
\item Behaviour of the food at large deformation?
\item How does food break into pieces?
\end{itemize}
\column{0.2\textwidth}
\includegraphics[width=\textwidth]{violon}
\end{columns}

@@

%
%
%
%\begin{frame}{Fundamental issues in biogels}
%\begin{itemize}
%\item Linear elasticity is not well understood \textit{\scriptsize Gardel et al. Science 2004}
%\item Strain and stress stiffening \textit{\scriptsize Storm et al. Nature 2005}
%\item Fractures \textit{\scriptsize Bonn et al. Science 1998, Baumberger et al. Nature Material 2006}
%\item Mechanical instabilities and morphogenesis \textit{\scriptsize Shyer et al. Science 2013}
%\end{itemize}
%\begin{tabu}{X[c]X[c]}
%\includegraphics[height=6\baselineskip]{Bonn_fracture} &
%\includegraphics[height=6\baselineskip]{Villi_sq}
%\end{tabu}
%\begin{block}{Our questions}
%\begin{itemize}
%\item What is the behaviour of a biogel under shear deep into the nonlinear regime?
%\item What is the role of the solvent in mechanical instabilities?
%\end{itemize}
%\end{block}
%\end{frame}

@@

\begin{frame}{Can we generalise to biogels? \textup{\normalsize(physical gels
$E_{bond}\gg k_B T$)}}
\begin{tabu}{cX[c]c}
\includegraphics[height=0.3\textheight]{cell_mech} &
\includegraphics[height=0.3\textheight]{electrophoresis} &
\includegraphics[height=0.3\textheight]{cosmetics} \\
Cell mechanics & Electrophoresis & Cosmetics\\
\end{tabu}
\begin{tabu}{X[c]X[c]}
\includegraphics[height=0.3\textheight]{bacterial_culture} &
\includegraphics[height=0.3\textheight]{food} \\
Bacterial culture & Food\\
\end{tabu}

\begin{footnotesize}
\begin{block}{Sources}
\begin{tabu}{lXl}
Wikimedia Commons & www.madaboutscience.com & www.keautystore.com\\
\end{tabu}
\end{block}
\end{footnotesize}
\end{frame}

\begin{frame}{Merciless yoghurt breakers}
\textit{Leocmach et al. PRL 113, 038303 (2014), \footnotesize ArXiv 1401.8234}

\bigskip
\begin{tabu}{X[c]X[c]c}
\includegraphics[height=0.3\textheight]{Chris}&
\includegraphics[height=0.3\textheight]{Thibaut}&
\includegraphics[height=0.3\textheight]{Seb}\\
Christophe Perge & Thibaut Divoux & Sebastien Manneville\\
PhD student & CNRS researcher & Professor\\
E.N.S. Lyon &  CRPP Bordeaux & E.N.S. Lyon\\
\end{tabu}

\bigskip
\begin{description}[Special thanks]
\item[Special thanks] to Alan Parker (Firmenich) for prompting this study and providing casein \& GDL
\end{description}

\end{frame}
